%-------------------------
% Resume in Latex
% Author : Farzad Hayat
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}
\usepackage[sfdefault]{roboto}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{linkblue}{RGB}{0, 102, 204}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=linkblue, urlcolor=linkblue, citecolor=linkblue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\linespread{1.15}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{5pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{https://linkedin.com/in/farzad-hayat/}{\Large Farzad Hayat}} & Email: \href{mailto:hello@farzadhayat.dev}{hello@farzadhayat.dev}\\
%   \href{https://farzadhayat.dev/}{farzadhayat.dev} & Mobile: \href{tel:+61422619437}{+61-422-619-437} \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Farzad Hayat} \\ \vspace{1pt}
    \small \textbf{\href{tel:+61422619437}{+61 422 619 437}} $|$ \textbf{\href{mailto:hello@farzadhayat.dev}{hello@farzadhayat.dev}} $|$
    \textbf{\href{https://www.linkedin.com/in/farzadhayat}{linkedin.com/in/farzadhayat}} $|$
    \textbf{\href{https://www.farzadhayat.dev}{farzadhayat.dev}} \\
    \vspace{1pt}
    \small NZ Citizen $|$ Available from June 2026
\end{center}


%-----------CAREER SUMMARY-----------
\section{Career Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    Final-semester Computer Science student at QUT (6.67 GPA) with hands-on experience shipping production features at Tanda, 15 months of QA engineering at Tiny Technologies, and practical expertise with AWS microservices. Seeking a full-time Software Engineering role from June 2026.
  }}
\end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Software Engineer Intern}{December 2025 -- January 2026}
        {Tanda}{Brisbane, Australia}
        \resumeItemListStart
            \resumeItem{Shipped the Compliance Document Library to production on Tanda's Ruby on Rails platform — a feature serving 10,000+ businesses to securely store, manage, and track critical compliance documents.}
            \resumeItem{Architected the PostgreSQL schema and automated email notification system for document expiry and required actions, ensuring quality through comprehensive Minitest tests and peer reviews in a two-person team.}
        \resumeItemListEnd

    \resumeSubheading
        {Quality Assurance Engineer}{December 2023 -- February 2025}
        {Tiny Technologies, TinyMCE}{Brisbane, Australia}
        \resumeItemListStart
            \resumeItem{Ensured stability for TinyMCE (2M+ monthly downloads) via end-to-end, smoke, and exploratory testing.}
            \resumeItem{Produced technical documentation for 23 releases and managed bug tracking using Jira, TestRail, and GitHub.}
        \resumeItemListEnd

    \resumeSubheading
        {Freelance IT Consultant}{September 2023 -- present}
        {Self-employed}{Remote}
        \resumeItemListStart
            \resumeItem{Built and deployed WordPress and cloud-hosted Windows Server infrastructure for Medics Online, a telehealth startup, supporting 800+ monthly patient appointment bookings from the company's inception.}
            \resumeItem{Configured server hosting, email infrastructure, and SEO to ensure reliable performance and discoverability.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Queensland University of Technology}{July 2021 -- June 2026}
      {Bachelor of Information Technology, Computer Science major}{Brisbane, Australia}
      \resumeItemListStart
        \resumeItem{6.67 / 7.00 GPA; Recipient of 3x QUT Executive Dean's Commendation for Academic Excellence.}
        \resumeItem{Interests: Cloud Computing, Systems Programming, Cyber Security, Machine Learning, Blockchain Technology.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{\href{https://github.com/adynsydeez/enviro-vision}{Project Pyro}} $|$ \emph{React, Python, FastAPI, Leaflet, Tailwind CSS, Claude Code}}{2026}
        \resumeItemListStart
            \resumeItem{Won Best Community Project at the QUT AIML Hackathon 2026 — built a browser-based wildfire simulation where players fight real Queensland bushfires on satellite maps.}
            \resumeItem{Implemented the Alexandridis cellular automata fire spread model on a 1,000×1,000 cell grid (10m resolution) incorporating wind speed, vegetation type, slope, and fuel moisture; rendered client-side with HTML5 Canvas at 500ms ticks across 1M cells.}
        \resumeItemListEnd

        \resumeProjectHeading
            {\textbf{\href{https://farzadhayat.dev/posts/cloud-transcriber/}{Cloud Media Transcriber}} $|$ \emph{AWS, Docker, Terraform, Node.js, Express, Postman, MongoDB, TensorFlow, Linux}}{2024}
        \resumeItemListStart
            \resumeItem{Architected a scalable media transcription pipeline using FFmpeg and Whisper ASR, orchestrating microservices via ECS/Lambda with an Express REST API behind an Nginx reverse proxy on EC2.}
            \resumeItem{Managed infrastructure-as-code with Terraform across 10+ AWS services (S3, SQS, Cognito, ElastiCache, CloudWatch) and stored transcription records in DocumentDB.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------CERTIFICATIONS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\href{https://www.credly.com/badges/4285aee7-9142-4f4a-9ee7-b862166762a9/linked_in_profile}{AWS Certified Cloud Practitioner}}{: July 2025 -- July 2028}
    }}
 \end{itemize}
 

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Ruby, JavaScript, SQL, C, C\#, Bash} \\
     \textbf{Frameworks \& Libraries}{: Ruby on Rails, Flask, JUnit}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
