%-------------------------
% Resume in Latex
% Author : Farzad Hayat
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4,11pt]{article}
\usepackage{lmodern}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{https://linkedin.com/in/farzad-hayat/}{\Large Farzad Hayat}} & Email: \href{mailto:farzad.hayat@outlook.com}{farzad.hayat@outlook.com}\\
%   \href{https://farzadhayat.dev/}{farzadhayat.dev} & Mobile: \href{tel:+61422619437}{+61-422-619-437} \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Farzad Hayat} \\ \vspace{1pt}
    \small \href{tel:+61422619437}{\underline{+61 422 619 437}} $|$ \href{mailto:farzad.hayat@outlook.com}{\underline{farzad.hayat@outlook.com}} $|$ 
    \href{https://linkedin.com/in/farzad-hayat}{\underline{linkedin.com/in/farzad-hayat}} $|$
    \href{https://farzadhayat.dev}{\underline{farzadhayat.dev}}
\end{center}


%-----------CAREER SUMMARY-----------
\section{Career Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    Final-year Bachelor of Information Technology student at QUT, majoring in Computer Science with a strong academic record and hands-on experience in cloud computing, DevOps, and software quality assurance. Completed 15 months as a QA Engineer and Technical Writer at Tiny Technologies, contributing to high-impact releases and cross-functional collaboration. Currently seeking a summer internship for 2025/2026 to apply and expand technical skills in a dynamic, real-world environment.
  }}
\end{itemize}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Queensland University of Technology}{July 2021 -- June 2026}
      {Bachelor of Information Technology, Computer Science major}{Brisbane, Australia (part-time, online)}
      \resumeItemListStart
        \resumeItem{6.67 / 7.00 GPA (Grade Point Average)}
        \resumeItem{Academic focus: Cloud Computing, Algorithms \& Data Structures, Systems Programming, Computer Networking}
        \resumeItem{Three-time recipient of QUT Executive Dean’s Commendation for Academic Excellence}
        \resumeItem{Developed leadership via College of Excellence workshops}
        \resumeItem{Active member of Code Network university club since 2023}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Quality Assurance Engineer}{December 2023 -- February 2025}
        {Tiny Technologies, TinyMCE}{Brisbane, Australia (part-time, hybrid)}
        \resumeItemListStart
            \resumeItem{Ensured product stability across TinyMCE’s high-traffic codebase (2M+ monthly downloads) by conducting end-to-end, smoke, and exploratory testing.}
            \resumeItem{Produced stakeholder-oriented technical documentation for 23 releases and 7 new plugins, improving clarity and adoption of new features.}
            \resumeItem{Streamlined issue traceability by managing bug tracking and development workflows using Jira, GitHub, and TestRail.}
            \resumeItem{Collaborated in agile sprints with engineers, designers, and testers to deliver iterative improvements and reduce release cycle time.}
        \resumeItemListEnd

    \resumeSubheading
        {Freelance IT Consultant}{September 2023 -- present}
        {Self-employed}{Brisbane, Australia (casual, remote)}
        \resumeItemListStart
            \resumeItem{Built and deployed a WordPress website for an Australian telehealth startup, enabling over 200 monthly patient interactions.}
            \resumeItem{Configured server hosting, email infrastructure, and SEO optimization to ensure reliable performance and strong online visibility.}
            \resumeItem{Provisioned cloud-hosted Windows Server environments to support practice management software and HotDoc integration, improving operational efficiency for medical staff.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{\href{https://farzadhayat.dev/posts/cloud-transcriber/}{\underline{Cloud Media Transcriber (Link)}}} $|$ \emph{AWS, Nginx, Express, Node.js, Docker, Terraform}}{2024}
        \resumeItemListStart
            \resumeItem{Developed a web application for media transcription, utilizing FFmpeg for audio conversion and Whisper ASR for transcribing audio to text.}
            \resumeItem{Designed and implemented a microservices architecture for efficient resource allocation and scalability, employing EC2 for the REST API and ECS with auto-scaling for CPU-intensive tasks.}
            \resumeItem{Utilized Lambda for event-driven tasks, integrated SQS queues for decoupled service communication, and managed user authentication with Cognito.}
            \resumeItem{Implemented robust security measures including HTTPS for data in transit and encryption at rest for S3 buckets and DocumentDB, securing sensitive information with Secrets Manager and Parameter Store.}
        \resumeItemListEnd
          
        \resumeProjectHeading
            {\textbf{\href{https://farzadhayat.dev/posts/ultimate-earth-championship/}{\underline{Ultimate Earth Championship (Link)}}} $|$ \emph{Java, Swing, JUnit, Agile, Git}}{2023}
        \resumeItemListStart
            \resumeItem{Engineered a Java-based game featuring character resurrection and melee combat, showcasing strong object-oriented design principles.}
            \resumeItem{Ensured software quality through rigorous unit and acceptance testing, contributing to a robust and reliable application.}
            \resumeItem{Applied Agile development methodologies to manage project timelines and deliver key milestones efficiently.}
        \resumeItemListEnd
          
    \resumeSubHeadingListEnd


%-----------CERTIFICATIONS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\href{https://www.credly.com/badges/4285aee7-9142-4f4a-9ee7-b862166762a9/linked_in_profile}{AWS Certified Cloud Practitioner}}{: Earned in July 2025, demonstrating strong foundational expertise in cloud computing and core AWS services.}
    }}
 \end{itemize}
 

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, SQL, JavaScript, Bash, C, C\#.} \\
     \textbf{Tools \& Frameworks}{: AWS, Linux, NodeJS, React, Terraform, TensorFlow, MongoDB, Figma, Kubernetes.}
    }}
 \end{itemize}


%-----------SOFT SKILLS-----------
\section{Soft Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Communication \& Collaboration}{: Clear stakeholder engagement, agile teamwork, and technical leadership across diverse teams.} \\
     \textbf{Problem Solving}{: Strategic troubleshooting, systems thinking, and modular design for scalable, maintainable solutions.} \\
     \textbf{Adaptability}{: Comfortable navigating hybrid work environments, learning new technologies, and balancing technical depth with user experience.}
    }}
 \end{itemize}


%-----------REFEREES-----------
\section{Referees}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{\textbf{Two referees available upon request}}}
\end{itemize}


%-------------------------------------------
\end{document}
